Exploring the internal language of toposes

### 2018-06-28 slides-como2018.tex
Slide on relations between the toposes

% Großer Zariskitopos
% Zusammenhang zum kleinen Topos
% Synthetische Quasikohärenz
% Klassifizierende Topoi

@@

@@

  \centering
  \hil{The mystery of nongeometric sequents}

>>>>

@@

\begin{frame}{Relations between the Zariski toposes}
  The big Zariski topos is a topos over the small Zariski topos:
  \[ \begin{array}{crcl}
    \pi : & \Zar(A) &\longrightarrow& \Spec(A) \\
    & \text{local~$A$-algebra~$(A \xrightarrow{\alpha} B)$} &\longmapsto& (A \to A[(\alpha^{-1}[B^\times])^{-1}])
  \end{array} \]
  This morphism is \hil{connected} ($\pi^{-1}$ is fully faithful) and
  \hil{local}, so there is a preinverse
  \[ \begin{array}{rcl}
    \Spec(A) &\longrightarrow& \Zar(A) \\
    \text{local localization~$(A \to B)$} &\longmapsto& (A \to B)
  \end{array} \]
  which is a subtopos inclusion inducing an idempotent monad~$\sharp$ and an
  idempotent comonad~$\flat$ on~$\Zar(S)$.

  \begin{itemize}
  \justifying
    \item Internally to~$\Zar(S)$, $\Spec(S)$ can be constructed as the
    \hil{largest subtopos} where~$\flat \affl \to \affl$ is bijective.
    \item Internally to~$\Spec(S)$, $\Zar(S)$ can be constructed as the
    \hil{classifying topos} of local~$\O_S$-algebras which are local over~$\O_S$.
    \item $\Zar(A)$ is the \hil{lax pullback}~$(\Set
    \Rightarrow_{\Set[\mathrm{Ring}]} \Set[\mathrm{LocRing}])$.
  \end{itemize}
\end{frame}

@@

  \centering
  \begin{varblock}{0.6344\textwidth}{}
    \centering
    \hil{the mystery of nongeometric sequents}
    \par
  \end{varblock}
